### 2024-08-17 paper.tex
more

\begin{lemma}
    \(V = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} V_{w,r}\).
    Further, \(V_{w_1r_1} = V_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \(\lambda_{w_1} = \lambda_{w_2} \land r_1 = r_2\).
    When \(V_{w_1r_1} \neq V_{w_2r_2}\), we have \(V_{w_1r_1} \cap V_{w_2r_2} = \emptyset\).
\end{lemma}
\begin{proof}
    TODO
\end{proof}
Now, fix any \(w\) and \(r\).
We will find the irreducible components of \(V_{w,r}\).
These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(V\) will be the irreducible components of \(V\).
\par Let 
\[G := \{P \in \GL_m : P^{-1} X P = X\},\]
and
\[G_{wr} := \{P \in \GL_m : \forall b. \exists b'. (P^{-1}, I_n) A_{e_{wr}, b} (P, I_n) = A_{e_{wr}, b'}\}.\]
If you write out the condition \(A_{e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\) as a matrix equation, it is plain to see that 
\[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
\par Now, define 
\[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]
Let \(G\) act on \(V_{wr}\) by
\[P \cdot (A_{e_{wr},b}, U) := ((P, I_n) A_{e_{wr}, b} (P, I_n)^{-1}, (P, I_n)U) = (A_{e_{wr} P^{-1}, Pb}, (P, I_n) U).\]
\par Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\) defined by
\[(x, P) \mapsto P \cdot x.\]
By restriction of \(G\) to \(G_{wr}\) and \(V_{wr}\) to \(U_{wr}\), we obtain an action of \(G_{wr}\) on \(U_{wr}\).
Then, letting \(G_{wr}\) act on \(G\) by left multiplication, we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).
\begin{lemma}
    The map \(\varphi\) is a topological quotient of \(U_{wr} \times G\) by the action of the algebraic group \(G_{wr}\).
\end{lemma}
\begin{proof}
    TODO.
    See \url{http://www-fourier.ujf-grenoble.fr/~mbrion/notes_luminy.pdf}, definition 1.18.
\end{proof}
Now we only have to find the irreducible components of \(U_{wr} \times G\)

\begin{lemma}
    Let \(p : X \to Y\) be a topological quotient.
    Then the irreducible components of \(Y\) are the images of those of \(X\).
\end{lemma}
\begin{proof}
    Let \(C_i\) be the irreducible components of \(X\).
\end{proof}

>>>>

\begin{lemma}
    \(V = \bigcup_{1 \leq w \leq k, 0 \leq r \leq \lambda_{w}} V_{w,r}\).
    Further, \(V_{w_1r_1} = V_{w_2r_2}\) exactly when either \(r_1 = r_2 = 0\), or \(\lambda_{w_1} = \lambda_{w_2} \land r_1 = r_2\).
    When \(V_{w_1r_1} \neq V_{w_2r_2}\), we have \(V_{w_1r_1} \cap V_{w_2r_2} = \emptyset\).
\end{lemma}
\begin{proof}
    TODO
\end{proof}
Now, fix any \(w\) and \(r\).
We will find the irreducible components of \(V_{w,r}\).
These will all happen to be equidimensional (with dimensions independent of \(w\) and \(r\)), so their closures in \(V\) will be the irreducible components of \(V\).
\par Let 
\[G := \{P \in \GL_m : P^{-1} X P = X\},\]
and
\[G_{wr} := \{P \in \GL_m : \forall b. \exists b'. (P^{-1}, I_n) A_{e_{wr}, b} (P, I_n) = A_{e_{wr}, b'}\}.\]
If you write out the condition \(A_{e_{wr}, b} (A, I_n) = (A, I_n) A_{X, e_{wr}, b'}\) as a matrix equation, it is plain to see that 
\[G_{wr} = \{A \in G : e_{wr}A = e_{wr}\}.\]
\par Now, define 
\[U_{wr} = \{(U, e_{wr}, b) \in V_{wr}\}.\]
Let \(G\) act on \(V_{wr}\) by
\[P \cdot (A_{e_{wr},b}, U) := ((P, I_n) A_{e_{wr}, b} (P, I_n)^{-1}, (P, I_n)U) = (A_{e_{wr} P^{-1}, Pb}, (P, I_n) U).\]
\par Consider the map \(\varphi : U_{wr} \times G \to V_{wr}\) defined by
\[(x, P) \mapsto P \cdot x.\]
By restriction of \(G\) to \(G_{wr}\) and \(V_{wr}\) to \(U_{wr}\), we obtain an action of \(G_{wr}\) on \(U_{wr}\).
Then, letting \(G_{wr}\) act on \(G\) by left multiplication, we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).
\begin{lemma}
    As an algebraic variety, \(G\) is irreducible.
\end{lemma}
\begin{proof}
    not sure why at the moment
\end{proof}
\begin{lemma}
    % The map \(\varphi\) is a geometric quotient of \(U_{wr} \times G\) by the action of the algebraic group \(G_{wr}\).
    The map \(\varphi\) is some sort of quotient by the action of \(G_{wr}\).
    % The map \(X \mapsto \overline{\varphi(X \times G)}\) is a bijection from the irreducible components of \(U_{wr}\) to the irreducible components of \(V_{wr}\).
\end{lemma}
\begin{proof}
    What kind?
    % Because \(X\) and \(G\) are irreducible, \(X \times G\) is irreducible, and therefore \(\varphi(X \times G)\) is, as well.
    % Let \(X_1, ..., X_k\) be the irreducible components of \(U_{wr}\).
    % It is clear that \(V_{mr} = \bigcup_i \overline{\varphi(X_i \times G)}\).
    % And if we take \(x \in X_i \setminus \bigcup_{j \neq i} X_j\), it is clear (since \(G\) acts faithfully on itself) that \(\varphi(x, I_m)\)
    % All that remains is to show that \(X_i \notin \bigcup_{j \neq i} \overline{\varphi(X_i \times G)}\).
    % Indeed, 
\end{proof}
Our strategy is to find the irreducible components \(X \subseteq U_{wr}\), and we will then argue that the irreducible components of \(V_{wr}\) are of the form \(\varphi(X \times G)\).
So, we will now find the irreducible components of \(U_{wr}\).
